### 2017-06-02 paper.tex
fixed DataCite url, added ORCID url

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give particular releases of lessons
DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://zenodo.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names and (where possible) identifiers like ORCIDs
should also be gathered for all contributors.

>>>>

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give particular releases of lessons
DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://www.datacite.org}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names and identifiers (e.g. ORCIDs (\url{https://orcid.org}))
should be gathered for all contributors.
